---
title: "Study4Analysis"
author: "TGoodge"
date: '2023-08-21'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#libraries
```{r}
library(tidyverse)
library(splitstackshape)
library(stringr)
library(data.table)
library(dplyr)
library(tidyr)
library(gridExtra)
library(lme4)
library(lmerTest)
library(afex)
library(effects)
library(ggplot2)
library(ggthemes)
library(report)
library(janitor)

```

#custom paletter
```{r}



C5_pal <- c("#0072B2","#D55E00","#009E73","#CC79A7","#56B4E9")

```



#read in data files
```{r}
dataFolder = "C:/Users/thoma/OneDrive - University of Glasgow/Desktop/Study 4/data/WHN/"

file_list <- list.files(path = dataFolder, pattern = "..csv$", all.files = TRUE, full.names = TRUE, recursive = TRUE) 
```

```{r read in raw data}
RawWHNDataset <- data.frame()
#loop through all the fills, create a temporary container, remove the first, second and last rows and then add 1 to the trials counter. Then bind it to the dataset
for (file in file_list){
  tempData <- read.csv(file, header = T)  
    
  RawWHNDataset <- bind_rows(RawWHNDataset, tempData)
}

```
#sort whn dataset
```{r subset bad ppts}
SortedWHNDataset <- RawWHNDataset  %>% 
  dplyr::select(participant,image_file,Correct,trials_3.thisTrialN, conf_slider.response, conf_slider.rt, MiseryScale.response, Attention_slider.response, trialResp.keys, trialResp.corr, trialResp.rt)

SortedWHNDataset$Attention_slider.response <- as.numeric(SortedWHNDataset$Attention_slider.response)

RawWHNDataset$trials_3.thisTrialN
SortedWHNDataset <- SortedWHNDataset %>%
#subset(image_file != "Slide24") %>%
  subset(participant != "P01") %>%
  subset(participant != "P02") %>%
  subset(participant != "P03") %>% 
  subset(participant != "P04") %>%
  subset(participant != "P05") %>%
  subset(participant != "P06") %>%
  subset(participant != "P13") %>%
  subset(participant != "P21") 
  
  
```
#read in counterbalancing
```{r add counterbalancing}
Counterbalancing <- read.csv("C:/Users/thoma/OneDrive - University of Glasgow/Desktop/Study 4/Study4Counterbalancing.csv", header = T)

Counterbalancing <- Counterbalancing %>%  dplyr::select(PID, First,Second,Third,Fourth)

Counterbalancing <- na.omit(Counterbalancing)

Counterbalancing$participant <- Counterbalancing$PID


```
#add counterbalancing order to dataset
```{r order the dataset}
OrderWHNDataset <- left_join(SortedWHNDataset, Counterbalancing, by = 'participant') 
OrderWHNDataset$Block <- 'Baseline' 


OrderWHNDataset$Block <-  if_else(OrderWHNDataset$trials_3.thisTrialN >= 30,OrderWHNDataset$Fourth,
                                  if_else(OrderWHNDataset$trials_3.thisTrialN >= 20,OrderWHNDataset$Third,
                                                  if_else(OrderWHNDataset$trials_3.thisTrialN >= 10,OrderWHNDataset$Second, 
                                                          OrderWHNDataset$First)))

OrderWHNDataset$trialResp.rt <-stringr::str_remove_all(OrderWHNDataset$trialResp.rt,"[\\[\\]]")
OrderWHNDataset$trialResp.rt <- as.numeric(OrderWHNDataset$trialResp.rt)

```



```{r}
WHNDataset <- OrderWHNDataset
WHNDataset <- WHNDataset[!is.na(WHNDataset$Correct),]

#WHNDataset <- left_join(WHNDataset, DemogDataOrg, by = "participant")
```
#Demographics
```{r}
  #Read in the data
  DemogDataRaw <- read.csv("C:/Users/thoma/OneDrive - University of Glasgow/Desktop/Study 4/data/Qualtrics/Demogs/TGStudy4Demogs.csv") %>%  
    select(starts_with('Q')) 
```
```{r}
#Change the first row into column headers
DemogDataOrg <- row_to_names(DemogDataRaw, row_number = 1)
#Remove consent form columns


```

#Frormat demographic data

```{r}
DemogDataOrg <- DemogDataOrg %>% 
  rename(Age = `What is your age?`) %>% 
  rename(Gender = `Which gender do you identify with?`) %>% 
  rename(UKLicense = `Do you have a UK driving license?`) %>%
  rename(CountryLicense = `Which country did you get your driving license in?`) %>%
  rename(YearsExp = `How many years driving experience do you have, either from when you passed your driving test or when you started driving regularly? (years / months)`) %>%
  rename(UKYearsExp = `How many years driving experience do you have in the UK (years, months)`) %>%
   rename(GlasgowYearsExp = `How many years driving experience do you have driving around the West End of Glasgow? (years, months)`) %>%
  
  rename(VideoGamesTime = `Approximately how many hours do you play video games for in an average week?`) %>% 
  rename(MotionSickness = `Do you have any history of motion sickness? - Selected Choice`) %>% 
  rename(MotionSicknessText = `Do you have any history of motion sickness? - Other (Please describe) - Text`) 

```


```{r}
DemogDataOrg$Age = as.numeric(DemogDataOrg$Age)
DemogDataOrg$VideoGamesTime = as.numeric(DemogDataOrg$VideoGamesTime)

DemogDataOrg$YearsExp = as.numeric(DemogDataOrg$YearsExp)

DemogDataOrg$UKYearsExp = as.numeric(DemogDataOrg$UKYearsExp)
DemogDataOrg$GlasgowYearsExp = as.numeric(DemogDataOrg$GlasgowYearsExp)

DemogDataOrg$Gender[DemogDataOrg$Gender == 'Woman'] <- 'Female'
DemogDataOrg$Gender[DemogDataOrg$Gender == 'Female '] <- 'Female'
DemogDataOrg$Gender[DemogDataOrg$Gender == 'Male '] <- 'Male'

DemogDataOrg <- DemogDataOrg %>%
  subset(participant != "P01") %>%
  subset(participant != "P02") %>%
  subset(participant != "P03") %>% 
  subset(participant != "P04") %>%
  subset(participant != "P05") %>%
  subset(participant != "P06") %>%
  subset(participant != "P13") %>%
  subset(participant != "P21") 

DemogDataOrg <- DemogDataOrg[!is.na(DemogDataOrg$Age),]

#table(DemogDataOrg$`How familiar are you with augmented reality (AR) prior to this experiment?`)

#table(DemogDataOrg$`How familiar are you with virtual reality (VR) prior to this experiment?`)



```
#Demog Summary
```{r}
DemogSummaryTotal <- DemogDataOrg %>% 
  
  summarise(
  n = n(),
  AgeMean = mean(Age, na.rm = T),
  AgeSD = sd(Age, na.rm = T),
  Male = sum(Gender == 'Male'),
  Female = sum(Gender == "Female"),
  UKLicense = sum(UKLicense == 'Yes'),
  UKExp = mean(UKYearsExp, na.rm = T),
  UKExpmin = min(UKYearsExp, na.rm = T),
  UKExpmax = max(UKYearsExp, na.rm = T),
  
  UKEXPsd = sd(UKYearsExp, na.rm = T),
  GlasgowExp = mean(GlasgowYearsExp, na.rm = T),
  GlasgowExpmin = min(GlasgowYearsExp, na.rm = T),
  GlasgowExpmax = max(GlasgowYearsExp, na.rm = T),
  GlasgowExpsd = sd(GlasgowYearsExp, na.rm = T),
  meanVG = mean(VideoGamesTime, na.rm = T),
  meanExp = mean(YearsExp, na.rm = T),
  minExp = min(YearsExp, na.rm = T),
  maxExp = max(YearsExp, na.rm = T),
  sdExp = sd(YearsExp, na.rm = T)

  )   
```

#Extract DBQ scores

```{r}
DBQ <- DemogDataOrg %>% 
  select(11: 37)

library(dplyr)
DBQ <- DBQ %>% mutate_all(list(~substr(., 1, 1))) 

IDs <- as.data.frame(WHNDataset$participant)

IDs <- IDs[!duplicated(IDs), ]
  
```

```{r}
DBQItems <- cols <- names(DBQ)

DBQ[DBQItems] <- lapply(DBQ[DBQItems], as.numeric)

DBQ$Errors <- 0
DBQ$Lapses <- 0
DBQ$Violations <- 0

DBQ$participant <- IDs

Errors <- DBQ %>% 
  select('participant', starts_with('E')) 
Errors$meanErrors = rowMeans(Errors[2:9])

Errors <- Errors %>% 
  select('participant', 'meanErrors')

Violations <- DBQ %>% 
  select('participant', starts_with('V')) 
Violations$meanViolations = rowMeans(Violations[2:9])

Violations <- Violations %>% 
  select('participant', 'meanViolations')



Lapses <- DBQ %>% 
  select('participant', starts_with('L')) 
Lapses$meanLapses = rowMeans(Lapses[2:9])

Lapses <- Lapses %>% 
  select('participant', 'meanLapses')
```
```{r}
DBQ <- left_join(DBQ, Errors, by = 'participant')

DBQ <- left_join(DBQ, Lapses, by = 'participant')

DBQ <- left_join(DBQ, Violations, by = 'participant')

medianError <- median(DBQ$meanErrors)
medianLapses <- median(DBQ$meanLapses)
medianViolation <- median(DBQ$meanViolations)


DBQ$ErrorGroup <-  ifelse(DBQ$meanErrors >= medianError, "High", "Low")
DBQ$LapseGroup <-  ifelse(DBQ$meanLapses >= medianLapses, "High", "Low")
DBQ$ViolationGroup <-  ifelse(DBQ$meanViolations >= medianViolation, "High", "Low")


```


```{r}
PptDBQ <- DBQ %>% 
  select(31:37)

WHNDataset <- left_join(WHNDataset, PptDBQ, by = 'participant')


```


```{r rename slides and factorise the data}
WHNDataset$participant <- as.factor(WHNDataset$participant)

WHNDataset$image_file[WHNDataset$image_file == "Slide1"] <- "Slide01"
WHNDataset$image_file[WHNDataset$image_file == "Slide2"] <- "Slide02"
WHNDataset$image_file[WHNDataset$image_file == "Slide3"] <- "Slide03"
WHNDataset$image_file[WHNDataset$image_file == "Slide4"] <- "Slide04"
WHNDataset$image_file[WHNDataset$image_file == "Slide5"] <- "Slide05"
WHNDataset$image_file[WHNDataset$image_file == "Slide6"] <- "Slide06"
WHNDataset$image_file[WHNDataset$image_file == "Slide7"] <- "Slide07"
WHNDataset$image_file[WHNDataset$image_file == "Slide8"] <- "Slide08"
WHNDataset$image_file[WHNDataset$image_file == "Slide9"] <- "Slide09"


WHNDataset$Block <- factor(WHNDataset$Block, levels = c("Control", "Cue",  "HUD", "HDD"))
```


```{r}
# WHNDataset$UKLicense[WHNDataset$UKLicense == "I have a license from another country"] <- "No"
# WHNDataset$UKLicense <- as.factor(WHNDataset$UKLicense)
```


```{r Create dataset with Cue as intercept}
WHNCuedDataset <- WHNDataset# %>% 
 # subset(Block != "Baseline")


WHNCuedDataset$Block <- factor(WHNCuedDataset$Block, levels = c("Cue","Control", "HUD", "HDD"))

```

```{r Create dataset with HUD as intercept}
WHNHUDDataset <- WHNDataset# %>% 
 # subset(Block != "Baseline")


WHNHUDDataset$Block <- factor(WHNHUDDataset$Block, levels = c("HUD","Control", "Cue", "HDD"))

```

```{r Create dataset with HDD as intercept}
WHNHDDDataset <- WHNDataset# %>% 
 # subset(Block != "Baseline")


WHNHDDDataset$Block <- factor(WHNHUDDataset$Block, levels = c("HDD", "HUD","Control", "Cue"))

```
```{r}
NoPpts <- n_distinct(WHNDataset$participant)

PPTWHNData <- WHNDataset[!duplicated(WHNDataset$participant), ]

NumHighErr <- sum(PPTWHNData$ErrorGroup == "High")
NumLowErr <- sum(PPTWHNData$ErrorGroup == "Low")

NumHighLap <- sum(PPTWHNData$LapseGroup == "High")
NumLowLap <- sum(PPTWHNData$LapseGroup == "Low")

NumHighVio <- sum(PPTWHNData$ViolationGroup == "High")
NumLowVio <- sum(PPTWHNData$ViolationGroup == "Low")



```
#WHN Summary
```{r summarise the data}
WHNSummary <- WHNDataset %>% 
  group_by(Block) %>% 
  summarise(n = (n()/NoPpts),
            WHN = sum(trialResp.corr / NoPpts ) ,
            WHNPercent = sum((trialResp.corr / NoPpts) /10) * 100,
            sdWHN = sd(trialResp.corr),
            seWHN = (sd(trialResp.corr))/ sqrt(NoPpts),
            meanConf = mean(conf_slider.response),
            sdConf = sd(conf_slider.response),
            seConf = (sd(conf_slider.response))/ sqrt(NoPpts),
            meanMISC = mean(MiseryScale.response),
            sdMISC = sd(MiseryScale.response),
            seMISC = (sd(MiseryScale.response))/ sqrt(NoPpts),
            meanAttention = mean(Attention_slider.response, na.rm = T),
            sdAttention = sd(Attention_slider.response, na.rm=T),
            seAttention = (sd(Attention_slider.response, na.rm=T))/ sqrt(NoPpts),
            trialRespmean = mean(trialResp.rt, na.rm=T),
            trialRespSD = sd(trialResp.rt, na.rm=T)
            )

CorrConfSummary <- WHNDataset %>% 
  group_by(Block, trialResp.corr) %>% 
  summarise(n = n(),
            conf = mean(conf_slider.response),
                        WHNPercent = sum((trialResp.corr / NoPpts) /10) * 100,
)

```


```{r}
write.csv(WHNDataset, "C:/Users/thoma/OneDrive - University of Glasgow/Desktop/Study 4/data/S4WHN.csv", row.names=FALSE)

```
#Clip Summaries
```{r}

ClipSummary <- WHNDataset %>% 
  group_by(image_file) %>% 
  summarise(n = n(),
            WHN = sum(trialResp.corr),
            sdWHN = sd(trialResp.corr))


ClipBlockSummary <- WHNDataset %>% 
  group_by(image_file, Block) %>% 
  summarise(n = n(),
            WHNCorr = sum(trialResp.corr),
            WHNIncorr = n() - sum(trialResp.corr),
            RatioCorr = WHNCorr / n() * 100,
            sdWHN = sd(trialResp.corr))

ClipConfSummary <- WHNDataset %>% 
  subset(Block == "Baseline") %>% 
  group_by(image_file) %>% 
  summarise(n = n(),
            WHNCorr = sum(trialResp.corr),
            WHNIncorr = n() - sum(trialResp.corr),
            RatioCorr = WHNCorr / n() * 100,
            conf = mean(conf_slider.response),
            sdWHN = sd(trialResp.corr))

```
#Clip Plots
```{r}
#library(ggpubfigs)

ggplot(data = ClipSummary, aes(x = image_file, y = WHN, fill = image_file))+
  geom_col()+
  theme(axis.text.x = element_text(angle = 90))+
  labs(xlim(0,NoPpts))+
  geom_hline(yintercept = NoPpts)+
    geom_hline(yintercept = NoPpts / 4)

ggplot(data = WHNDataset, aes(x = image_file, y = conf_slider.response, fill = image_file))+
  geom_boxplot()+
  theme(axis.text.x = element_text(angle = 90))+
  labs(xlim(0,1))

ggplot(data = ClipBlockSummary, aes(x = image_file, y = WHNCorr, fill = Block))+
  geom_col()+
  theme(axis.text.x = element_text(angle = 90))+
  labs(xlim(0,NoPpts))+
  geom_hline(yintercept = NoPpts, colour = 'blue')+
  geom_hline(yintercept = NoPpts / 4, colour = 'red', linetype = 'dashed')


```

```{r}
AttSum <- WHNDataset %>% 
  group_by(Block) %>% 
  summarise(n = NoPpts,
            mean = mean(Attention_slider.response, na.rm = T),
            sd = sd(Attention_slider.response, na.rm = T))
```
#WHN Col Plot
```{r}

WHNBaseline <- as.numeric(WHNSummary[1,3])

ggplot(data = WHNSummary, aes(x = Block, y = WHN, fill = Block))+
  geom_col()+
  geom_errorbar(aes(ymin = WHN - sdWHN, ymax = WHN + sdWHN),
                width = 0.2, 
                position = position_dodge(0.9))+
  geom_hline(yintercept = WHNBaseline, linetype = "dashed", size = 0.5)+
  #geom_hline(yintercept = 8, linetype = "solid", size = 1.0)+
  #geom_hline(yintercept = 2, linetype = "dotted", size = 1.0)+
  labs(title = "Average Hazard Prediction Score", x = "NDRT Presentation Condition", y = "Average number of correct responses")+
  ylim(0,8)+
  scale_fill_hue(l = 40)


ggplot(data = WHNDataset, aes(x = Block, y = trialResp.corr, fill = Block))+
  stat_summary()
```
#WHN Boxplots
```{r}



PlotData <- WHNDataset %>% 
  select(participant, trialResp.corr, trials_3.thisTrialN, Block) %>%   group_by(participant, Block) %>% 
  summarise(participant = participant,
            score = sum(trialResp.corr),
            Block = Block)

WHNPlot2 <- ggplot(data = PlotData, aes(x = Block, y = score, fill = Block))+
  geom_violin(alpha = 0.8)+
  geom_boxplot(alpha = 0, width = 0.2)+
  #scale_fill_manual(values = friendly_pal("ito_seven"))+
  scale_fill_brewer(palette = "RdYlBu")+
    labs( x = "NDRT Presentation Condition", y = "Average number of correct responses")+

    theme_classic()+
theme(legend.position="none") +theme(text=element_text(size = 20)) +

  theme(axis.text=element_text(size=15))+
    theme(plot.title=element_text(vjust=11.5))+

  theme(plot.margin =unit(c(2,0,0,0),"cm"))

"#0072B2"
"#D55E00"
"#009E73"
"#CC79A7"
"#56B4E9" 
"#E69F00" 
"#F0E442"

#7D3C98

WHNPlot2

ggsave(filename = "TAPSWHNPlot.png",
       plot = WHNPlot2,
       scale = 3,
       device = png,
       units = "px",
       dpi = 700)
```


```{r}
ggplot(data = PlotData, aes(x = Block, y = score, fill = Block))+
  geom_violin(alpha = 0.8)+
  geom_boxplot(alpha = 0, width = 0.2)+
    theme_classic()+
  ylab("Average Study 4 WHN Score")+
  xlab("AR Presentation Condition")

```

```{r}
WHNAOV <- glm(family = binomial, data = WHNDataset, formula = trialResp.corr ~ Block)

summary(WHNAOV)

```

#######CONFIDENCE SCORES##############
```{r}
ConfBaseline <- as.numeric(WHNSummary[1,7])


ggplot(data = WHNSummary, aes(x = Block, y = meanConf, fill = Block))+
  geom_col()+
  geom_errorbar(aes(ymin = meanConf - sdConf/2, ymax = meanConf + sdConf/2),
                width = 0.2, 
                position = position_dodge(0.9))+
  geom_hline(yintercept = ConfBaseline, linetype = "dashed", size = 1.0)+
  labs(title = "Average Confidence Score", y = "Mean Confidence Rating", x = "NDRT Presentation Condition")+
  ylim(0,1.0)+
  scale_fill_hue(l = 40)

ConfBaseline <- as.numeric(WHNSummary[1,7])


ConfPlot2 <- ggplot(data = WHNDataset, aes(x = Block, y = conf_slider.response, fill = Block))+
  geom_violin(alpha = 0.8) + geom_boxplot(alpha=0.2, width = 0.2)+
  labs(title = "Average Confidence Score", y = "Mean Confidence Rating", x = "", key= FALSE)+
  ylim(0,1.0)+
   scale_fill_manual(values = friendly_pal("ito_seven"))+
  theme_classic()+
  theme(legend.position="none")+
  theme(text=element_text(size = 15)) +
  theme(axis.text=element_text(size=10))+
  theme(plot.title=element_text(vjust=14))+

  theme(plot.margin =unit(c(2,0,0,0),"cm"))


ConfPlot2

```



###########MISC SCORES###########

```{r}
MISCDataset <- WHNDataset %>%
  group_by(trials_3.thisTrialN, Block) %>%
  summarise(mean = mean(MiseryScale.response),
            sd = sd(MiseryScale.response)) 


ggplot(data = MISCDataset, aes(x = trials_3.thisTrialN, y = mean))+
  geom_line(aes(colour  = factor(Block)))+
  geom_point(aes(colour = Block))+
  geom_ribbon(aes(ymin =MISCDataset$mean - MISCDataset$sd, ymax = MISCDataset$mean + MISCDataset$sd, fill = Block),alpha= 0.0) +  
  labs(title = "MISC Score")


```


```{r Separate MISC data}
MISCARDataset <- MISCDataset %>% 
  subset(Block != "Cue") %>% 
  subset(Block != "HDD") %>% 
  subset(Block != "Control") 

MISCCueDataset <- MISCDataset %>% 
  subset(Block != "HUD") %>% 
  subset(Block != "HDD") %>% 
  subset(Block != "Control") 

MISCHDDDataset <- MISCDataset %>% 
  subset(Block != "HUD") %>% 
  subset(Block != "Cue") %>% 
  subset(Block != "Control") 

```

```{r plot each condition's MISC scores}
ggplot(data = MISCARDataset, aes(x = trials_3.thisTrialN, y = mean))+
  geom_line(aes(colour  = factor(Block)))+
  geom_point(aes(colour = Block))+
  geom_ribbon(aes(ymin =MISCARDataset$mean - MISCARDataset$sd, ymax = MISCARDataset$mean + MISCARDataset$sd, fill = Block),alpha= 0.2) +  
  geom_vline(xintercept = 10)+
  geom_vline(xintercept = 20)+
  geom_vline(xintercept = 30)+
  labs(title = "MISC Score - AR HUD")+
  scale_x_continuous(breaks = seq(0, 40, 10))

ggplot(data = MISCCueDataset, aes(x = trials_3.thisTrialN, y = mean))+
  geom_line(aes(colour  = factor(Block)))+
  geom_point(aes(colour = Block))+
  geom_ribbon(aes(ymin =MISCCueDataset$mean - MISCCueDataset$sd, ymax = MISCCueDataset$mean + MISCCueDataset$sd, fill = Block),alpha= 0.2) +  
    geom_vline(xintercept = 10)+
  geom_vline(xintercept = 20)+
  geom_vline(xintercept = 30)+
  labs(title = "MISC Score - Cued AR HUD")+
  scale_x_continuous(breaks = seq(0, 40, 10))


ggplot(data = MISCHDDDataset, aes(x = trials_3.thisTrialN, y = mean))+
  geom_line(aes(colour  = factor(Block)))+
  geom_point(aes(colour = Block))+
  geom_ribbon(aes(ymin =MISCHDDDataset$mean - MISCHDDDataset$sd, ymax = MISCHDDDataset$mean + MISCHDDDataset$sd, fill = Block),alpha= 0.2) +  
    geom_vline(xintercept = 10)+
  geom_vline(xintercept = 20)+
  geom_vline(xintercept = 30)+
  labs(title = "MISC Score - HDD ")+
  scale_x_continuous(breaks = seq(0, 40, 10))



```

```{r}
AttBaseline <- as.double(AttSum[1,3])

ggplot(data = AttSum, aes(x = Block, y = mean, fill = Block))+
  geom_col()+
  geom_errorbar(aes(ymin = mean - sd, ymax = mean + sd),
                width = 0.2, 
                position = position_dodge(0.9))+
  labs(title = "Subjective Attention Rating", y = "Mean Attention Rating", x = "NDRT Presentation Condition")+
  geom_hline(yintercept = AttBaseline, linetype = "dashed", size = 1.0)+
  scale_fill_hue(l = 40)

AttBaseline <- as.double(AttSum[1,3])

AttPlot2 <- ggplot(data = WHNDataset, aes(x = Block, y = Attention_slider.response, fill = Block))+
  geom_violin(alpha = 0.8)+geom_boxplot(alpha = 0.2, width = 0.2)+
 
  labs(title = "Subjective Attention Rating", y = "Mean Attention Rating", x = "NDRT Presentation Condition")+
    scale_fill_manual(values = friendly_pal("ito_seven"))+
    theme_classic()+
theme(legend.position="none")+
  theme(text=element_text(size = 15))+
  theme(plot.title=element_text(vjust=14))+
  theme(axis.text=element_text(size=10))+
  theme(plot.margin =unit(c(2,0,0,0),"cm"))

  AttPlot2
  

```
```{r group all graphs together}
library(cowplot)

subPlot<- plot_grid(ConfPlot2, AttPlot2, labels = c('b)','c)'),ncol = 1)

subPlot


legend_b <- get_legend(
  WHNPlot2 + 
    guides(color = guide_legend(nrow = 1)) +
   theme(legend.position = "bottom")
)

FullPlot <- plot_grid(WHNPlot2, subPlot, labels = ('a)'))

FinalPlot <- plot_grid(FullPlot, legend_b, ncol = 1, rel_heights = c(1, .1))

FinalPlot

file1 <- tempfile("file1", fileext = ".png")

width = 1920

ggsave(filename = "FullPlot2.png",
       plot = FinalPlot,
       scale = 3,
       device = png,
       width = 3840,
       units = "px",
       dpi = 700)

```
#WHN Stats
```{r}
WHNNullModel0 <- glmer(data = WHNDataset, formula = trialResp.corr ~ 1 + (1|participant) + (1|image_file) , family = binomial, glmerControl( optimizer = "bobyqa"))

WHNModel <- glmer(data = WHNDataset, formula = trialResp.corr ~  Block  + (1|image_file) , family = binomial, glmerControl( optimizer = "bobyqa"))

WHNModelBasic <- glmer(data = WHNDataset, formula = trialResp.corr ~  Block + (1 |participant) + (1|image_file) , family = binomial, glmerControl( optimizer = "bobyqa"))

WHNModel1 <- glmer(data = WHNDataset, formula = trialResp.corr ~  Block + (1 + Block|participant)  , family = binomial, glmerControl( optimizer = "bobyqa"))

WHNModel2 <- glmer(data = WHNDataset, formula = trialResp.corr ~  Block + (1 + Block|participant) + (1|image_file) , family = binomial, glmerControl( optimizer = "bobyqa"))

WHNModel3 <- glmer(data = WHNDataset, formula = trialResp.corr ~  Block + (1 + Block|participant) + (1 + Block|image_file) , family = binomial, glmerControl( optimizer = "bobyqa"))

WHNModel4 <- glmer(data = WHNDataset, formula = trialResp.corr ~  Block  + meanViolations + (1|image_file)  , family = binomial, glmerControl( optimizer = "bobyqa"))

summary(WHNModel4)

summary(WHNModelBasic)
library(effects)

ef <- as.data.frame(effect("Block", WHNModelBasic))
head(ef)

library(report)
#WHNResults <- report(WHNModelBasic, CI = 95)
# ef <- as.data.frame(effect("Block", CueWHNModel2))
# 
# head(ef)
summary(WHNResults)

anova(WHNModel, WHNModelBasic, WHNModel1, WHNModel2, WHNModel3)

anova(WHNModelBasic, WHNModel2)
```

```{r}
library(MuMIn)
r.squaredGLMM(WHNModelBasic, WHNNullModel0)

```
```{r}
ef <- as.data.frame(effect("Block", WHNModel2))

head(ef)


ggplot(ef, aes(Block, fit, color=fit)) + 
  geom_pointrange(aes(ymax=upper, ymin=lower), position=position_dodge(width = 0.2))+
  theme_classic() # just for a change :)
```

```{r Cued WHN GLMERS}

CueWHNModelNull = glmer(data = WHNCuedDataset, formula = trialResp.corr ~ 1  +  + (1|participant) + (1|image_file),family = binomial,glmerControl(optimizer = "bobyqa"))
#summary(CueWHNModelNull)

CueWHNModel = glmer(data = WHNCuedDataset, formula = trialResp.corr ~  Block + (1 + Block|participant) + (1|image_file) , family = binomial, glmerControl( optimizer = "bobyqa"))


#summary(CueWHNModel1)

#CueWHNModel2 = glmer(data = WHNCuedDataset, formula = trialResp.corr ~ Block + (1|participant) + (1|image_file) + (Block|image_file),family = binomial, control = glmerControl(optimizer="bobyqa"))
#summary(CueWHNModel2)

#anova(CueWHNModel1, CueWHNModel, CueWHNModel2)#, CueWHNModel2)
summary(CueWHNModel)

CueResults <- report(CueWHNModel, CI = (95))
# ef <- as.data.frame(effect("Block", CueWHNModel2))
# 
# head(ef)
summary(CueResults)

r.squaredGLMM(CueWHNModel2, CueWHNModelNull)


```


```{r HUD WHN GLMERS}

HUDWHNModelNull = glmer(data = WHNHUDDataset, formula = trialResp.corr ~ 1 + (1|participant) + (1|image_file),family = binomial,glmerControl(optimizer = "bobyqa"))
#summary(HUDWHNModelNull)

HUDWHNModel1 = glmer(data = WHNHUDDataset, formula = trialResp.corr ~ Block + (1|participant) + (1|image_file),family = binomial,glmerControl(optimizer = "bobyqa"))
#summary(HUDWHNModel1)

anova(HUDWHNModelNull,HUDWHNModel1)

summary(HUDWHNModel1)

HUDResults <- report(HUDWHNModel1, CI = 95)

print(HUDResults)


```

```{r HDD WHN GLMER}

HDDWHNModelNull = glmer(data = WHNHDDDataset, formula = trialResp.corr ~ 1 + (1|participant) + (1|image_file),family = binomial, glmerControl(optimizer = "bobyqa"))
#summary(HUDWHNModelNull)

HDDWHNModel1 = glmer(data = WHNHDDDataset, formula = trialResp.corr ~ Block + (1|participant) + (1|image_file),family = binomial, glmerControl(optimizer = "bobyqa"))

HDDWHNModel = glmer(data = WHNHDDDataset, formula = trialResp.corr ~ Block  + (1|image_file),family = binomial, glmerControl(optimizer = "bobyqa"))

summary(HDDWHNModel1)

anova(HDDWHNModelNull,HDDWHNModel, HDDWHNModel1)

HDDResults <- report(HDDWHNModel, CI = 95)

print(HDDResults)

```

#CONFIDENCE Stats
```{r}
ConfNullModel <- glmer(data = WHNDataset, formula = conf_slider.response ~  (1|participant) + (1|image_file), family = binomial)

summary(ConfNullModel)
```

```{r}

ConfModel = lmer(data = WHNDataset, formula = conf_slider.response ~ Block + (1|participant) + (1|image_file), ontrol(optimizer = "bobyqa"))
summary(ConfModel)

ConfModel1 = lmer(data = WHNDataset, formula = conf_slider.response ~ Block + (1|participant) + (1|image_file),  family = binomial, glmerControl(optimizer = "bobyqa"))
summary(ConfModel1)

ConfModel2 = lmer(data = WHNDataset, formula = conf_slider.response ~ Block + (1|participant) + (1 + Block|image_file), family = binomial, glmerControl(optimizer = "bobyqa"))

ConfModel3 = lmer(data = WHNDataset, formula = conf_slider.response ~ Block + (1 + Block|participant) + (1 + Block|image_file),family = binomial, glmerControl(optimizer = "bobyqa"))

summary(ConfModel1)

anova(ConfModel1, ConfModel2, ConfModel3)

r.squaredGLMM(ConfModel1, ConfNullModel)
```

```{r Conf GLMER Summary}

Confresults <- report(ConfModel1, CI = 95)

summary(ConfModel1)

fixef(ConfModel1)

print(Confresults)
#anova(Model1)

efconf <- as.data.frame(effect("Block", ConfModel1))
head(efconf)

```

```{r}
ConfCueModel1 = glmer(data = WHNCuedDataset, formula = conf_slider.response ~ Block + (1|participant) + (1|image_file), family = binomial, glmerControl(optimizer = "bobyqa"))

summary(ConfCueModel1)

ConfCueresults <- report(ConfCueModel1, CI = 95)

print(ConfCueresults)
#anova(Model1)

```

```{r}

ConfHUDModel1 = glmer(data = WHNHUDDataset, formula = conf_slider.response ~ Block + (1|participant) + (1|image_file), family = binomial, glmerControl(optimizer = "bobyqa"))

summary(ConfHUDModel1)

fixef(ConfHUDModel1)


ConfHUDresults <- report(ConfHUDModel1, CI = 95)

print(ConfHUDresults)
#anova(Model1)

```

```{r}

ConfHDDModel1 = glmer(data = WHNHDDDataset, formula = conf_slider.response ~ Block + (1|participant) + (1|image_file), family = binomial, glmerControl(optimizer = "bobyqa"))

summary(ConfHDDModel1)

fixef(ConfHDDModel1)


ConfHDDresults <- report(ConfHDDModel1, CI = 95)

print(ConfHDDresults)
#anova(Model1)

```


#Confidence expand Corr
```{r}
WHNCorr <- WHNDataset %>% 
  subset(trialResp.corr == 1)

WHNCorr$Block <- relevel(WHNCorr$Block, ref = "Control")


CorrConfModel = glmer(data = WHNCorr, formula = conf_slider.response ~ Block + (1|participant) + (1|image_file),  family = binomial, glmerControl(optimizer = "bobyqa"))
summary(CorrConfModel)


```

#Confidence expand Incorrect
```{r}
WHNIncorr <- WHNDataset %>% 
  subset(trialResp.corr == 0)

WHNIncorr$Block <- relevel(WHNIncorr$Block, ref = "Control")


IncorConfModel = glmer(data = WHNIncorr, formula = conf_slider.response ~ Block + (1|participant) + (1|image_file),  family = binomial, glmerControl(optimizer = "bobyqa"))
summary(IncorConfModel)

```







```{r}

MISCNullModel <- glmer(data = WHNDataset, formula = MiseryScale.response ~ 1 + (1|participant), family = poisson)

summary(MISCNullModel)

```

```{r}
MISCModel1 = glmer(data = WHNDataset, formula = MiseryScale.response ~ Block + (1|participant) , family = poisson)

summary(MISCModel1)
```


```{r}
MISCresults <- report(MISCModel1, CI = 95)

print(MISCresults)

```


```{r}
AttentionDataset <- WHNDataset %>% 
  subset(!is.na(Attention_slider.response))


AttentionDataset$Block <- factor(AttentionDataset$Block, levels = c("Control","Cue", "HUD", "HDD"))

AttAOV <- aov(data = AttentionDataset,formula =  Attention_slider.response ~ Block)

TukeyHSD(AttAOV)
```

```{r}
AttentionSummary <- AttentionDataset %>% 
  group_by(Block) %>% 
summarise(n = n(),
          mean = mean(Attention_slider.response),
          sd = sd(Attention_slider.response))


```

```{r}

ggplot(AttentionDataset, aes(x=Attention_slider.response)) +
    geom_histogram(binwidth=0.1, colour="black", fill="white")

library(rstatix)
AttentionDataset %>% 
  group_by(Block) %>% 
  identify_outliers(Attention_slider.response)

AttentionDataset %>% 
  group_by(Block) %>% 
  shapiro_test(Attention_slider.response)

library(ggpubr)

ggqqplot(AttentionDataset, "Attention_slider.response", facet.by = "Block")
```

```{r}
Att.aov <- anova_test(data = AttentionDataset, dv = Attention_slider.response, wid = participant, within = Block)

get_anova_table(Att.aov)

pwc <- AttentionDataset %>% 
  pairwise_t_test(Attention_slider.response ~ Block, paired = TRUE,
                  p.adjust.method = "bonferroni")

pwc <- pwc %>%  add_xy_position(x = "Block")



bxp <- ggboxplot(AttentionDataset, x = "Block", y = "Attention_slider.response", add = "point")

bxp + 
  #stat_pvalue_manual(pwc) +
  labs(
    subtitle = get_test_label(Att.aov, detailed = TRUE),
    caption = get_pwc_label(pwc)
  )


```

```{r}
AttentionCuedDataset <- AttentionDataset# %>% 
 # subset(Block != "Baseline")


AttentionCuedDataset$Block <- factor(AttentionCuedDataset$Block, levels = c("Cue","Control", "HUD", "HDD"))

AttentionHUDDataset <- AttentionDataset# %>% 
 # subset(Block != "Baseline")


AttentionHUDDataset$Block <- factor(AttentionHUDDataset$Block, levels = c("HUD","Control", "Cue", "HDD"))

AttentionHDDDataset <- AttentionDataset# %>% 
 # subset(Block != "Baseline")


AttentionHDDDataset$Block <- factor(AttentionHDDDataset$Block, levels = c("HDD", "HUD","Control", "Cue"))


AttentionTabletDataset <- AttentionDataset# %>% 
 # subset(Block != "Baseline")



```
#Attention Glmers
```{r}
AttModel1 <- glmer(family = binomial, data = AttentionDataset, formula = Attention_slider.response ~ Block + (1|participant), glmerControl(optimizer = "bobyqa"))

AttModel2 <- glmer(family = binomial, data = AttentionDataset, formula = Attention_slider.response ~ Block + (1|participant) + (1|trials_3.thisTrialN), glmerControl(optimizer = "bobyqa"))

AttModel3 <- glmer(family = binomial, data = AttentionDataset, formula = Attention_slider.response ~ Block + conf_slider.response + (1|participant) , glmerControl(optimizer = "bobyqa"))

summary(AttModel1)

summary(AttModel2)

summary(AttModel3)

anova(AttModel1, AttModel)

AttResults <- report(AttModel1, CI = 95)

print(AttResults)


```

```{r}

AttCueAOV <- glm(family = binomial, data = AttentionCuedDataset, Attention_slider.response ~ Block )
summary(AttCueAOV)

AttHUDAOV <- glm(family = binomial, data = AttentionHUDDataset, Attention_slider.response ~ Block )

summary(AttHUDAOV)

AttHDDAOV <- glm(family = poisson, data = AttentionHDDDataset, Attention_slider.response ~ Block )

summary(AttHDDAOV)


```


```{r}


AttHDDAOV <- glm(family = poisson, data = AttentionHDDDataset, Attention_slider.response ~ Block )

summary(AttHDDAOV)


```

```{r}
ggplot(WHNDataset, aes(x = Block, y = Attention_slider.response, color=Block)) + 
  stat_summary(fun=mean, geom="point", size=3) + 
  stat_summary(fun.data=mean_se, geom="errorbar", width=0.2) + 
  stat_summary(aes(y=fitted(WHNModelBasic)), fun=mean, geom="line") +
  labs(x="QType", y="SCORE", 
       color="Exposure\n(Tertiles)") + 
  theme_bw()
```


```{r}
FullWHN <-  read.csv("C:/Users/thoma/OneDrive - University of Glasgow/Desktop/Study 4/data/WHNScores.csv")

```


```{r}
ggplot(FullWHN, aes(x=trialResp.corr)) +
    geom_histogram(binwidth=0.1, colour="black", fill="white")

library(rstatix)
FullWHN %>% 
  group_by(Study) %>% 
  identify_outliers(trialResp.corr)

FullWHN %>% 
  group_by(Study) %>% 
  shapiro_test(trialResp.corr)

library(ggpubr)

ggqqplot(FullWHN, "trialResp.corr", facet.by = "Study")
```

```{r}


FullWHNaov <- aov(formula = trialResp.corr ~  Study * Block , data = FullWHN)

pairs <- TukeyHSD(FullWHNaov, which = 'Block')
TukeyHSD(FullWHNaov, which = 'Study')

pairs

summary(FullWHNaov)

emmeans(FullWHNaov)

FullWHNSummary<- FullWHN %>% 
  group_by(participant, Study, Block) %>% 
  summarise(NumCorr = sum(trialResp.corr == 1),
            Total = sum(trialResp.corr ==1 | trialResp.corr == 0),
            Prop = NumCorr / Total * 100)


FullWHNOverall <- FullWHNSummary %>% 
  group_by(Study, Block) %>% 
    summarise(Total = mean(Prop))


FullWHNaov <- aov(formula = Prop ~  Study * Block , data = FullWHNSummary)

summary(FullWHNaov)



```
```{r}
FullWHNaov <- anova_test(data = FullWHN, dv = trialResp.corr, between = Study)

get_anova_table(FullWHNaov)

FullWHNpwc <- FullWHN %>% 
  pairwise_t_test(trialResp.corr ~ Study, paired = TRUE,
                  p.adjust.method = "bonferroni")

FullWHNpwc <- FullWHNpwc %>%  add_xy_position(x = "Study")

FullWHNpwc

FullWHNbxp <- ggboxplot(FullWHN, x = "Study", y = "trialResp.corr", add = "point")

FullWHNbxp + 
  #stat_pvalue_manual(pwc) +
  labs(
    subtitle = get_test_label(FullWHNaov, detailed = TRUE),
    caption = get_pwc_label(FullWHNpwc)
  )


```


```{r}


FullConfWHNaov <- aov(formula = conf_slider.response ~  Study * Block , data = FullWHN)

Confpairs <- TukeyHSD(FullConfWHNaov, which = 'Block')

Confpairs



```

```{r}


FullAttWHNaov <- aov(formula = Attention_slider.response ~  Study * Block , data = FullWHN)

Attpairs <- TukeyHSD(FullAttWHNaov, which = 'Block')

Attpairs



```
#######DBQ Comparisons###########

```{r}
ErrorWHNaov <- aov(data = WHNDataset, formula = trialResp.corr ~ Block * ErrorGroup)
summary(ErrorWHNaov)

LapseWHNaov <- aov(data = WHNDataset, formula = trialResp.corr ~ Block * LapseGroup)
summary(LapseWHNaov)

ViolationWHNaov <- aov(data = WHNDataset, formula = trialResp.corr ~ Block * ViolationGroup)
summary(ViolationWHNaov)

```



```{r}
Erroraov <- aov(data = WHNDataset, formula = trialResp.rt ~ Block * ErrorGroup)
summary(Erroraov)

Lapseaov <- aov(data = WHNDataset, formula = trialResp.rt ~ Block * LapseGroup)
summary(Lapseaov)

TukeyHSD(Lapseaov, which = "LapseGroup")


Violationaov <- aov(data = WHNDataset, formula = trialResp.rt ~ Block * ViolationGroup)
summary(Violationaov)

```
```{r}
ErrorConfaov <- aov(data = WHNDataset, formula = conf_slider.response ~ Block * ErrorGroup)
summary(ErrorConfaov)

LapseConfaov <- aov(data = WHNDataset, formula = conf_slider.response ~ Block * LapseGroup)
summary(LapseConfaov)

TukeyHSD(LapseConfaov, which = "LapseGroup")

ViolationConfaov <- aov(data = WHNDataset, formula = conf_slider.response ~ Block * ViolationGroup)
summary(ViolationConfaov)

```

```{r}
ErrorAttaov <- aov(data = WHNDataset, formula = Attention_slider.response ~ Block * ErrorGroup)
summary(ErrorAttaov)

LapseAttaov <- aov(data = WHNDataset, formula = Attention_slider.response ~ Block * LapseGroup)
summary(LapseAttaov)

TukeyHSD(LapseAttaov, which = "LapseGroup")

ViolationAttaov <- aov(data = WHNDataset, formula = Attention_slider.response ~ Block * ViolationGroup)
summary(ViolationAttaov)

```

